---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Examining Repressive and Oppressive State Violence using the Ill-Treatement Contents and Torture Data

This repo contains replication materials for:

Beger, Andreas and Daniel W. Hill, Jr., 20XX, "Examining Repressive and Oppressive State Violence using the Ill-Treatement Contents and Torture Data", _Conflict Managament and Peace Science_. 

```bibtex
@article{beger20XXexamining,
  author = {Andreas Beger and Daniel W.\ Hill, Jr.\},
  title = {Examining Repressive and Oppressive State Violence using the Ill-Treatement Contents and Torture Data},
  year = ,
  journal = {Conflict Management and Peace Science},
  volume = {},
  number = {},
  doi = {}
}
```

## Code

The R scripts in the `R/` folder replicate the figures and tables in the main paper and supplemental appendix. The `R/functions.R` file contains helper functions used in some of the other scripts, otherwise all the other files can be run in the order they sort alphabetically. 

Files that start with `si`...pertain to the SI. All other files are related to the main article. 

All output generated by the scripts will be saved in the `output/` folder and sub-folders. It should have the following structure:

```
- output/
  - figures/
  - figures-si/
  - models/
  - tables/
```

Training the XGBoost model (`2-xgboost.R`) and the SI expanded model set (`si1-estimate-all-models.R`) takes a while. We have included the trained XGBoost model in `output/mdl-xgboost.rds` and thus it is possible to replicate the main results without re-training it. There are 1,008 models in the SI. These are not included, but estimating them does not take quite as long as training the XGBoost model. 

## Data

The data is included in the `data` directory both in R's native RDS format and in CSV form. 

Most variables have prefixes indicating the data source:

- `itt_`: Ill-Treatment and Torture data; also binary indicators starting with `yy_` and used in an earlier version
- `NY.GDP.MKTP.KD` and subequent, including `pop`: World Bank World Development Indicators
- `v2x_`: V-Dem
- `regime` and `dd_democracy` from Cheibub, Gandhi, and Vreeland Democracy and dictatorships data
- `epr_`: Ethnic Power Relations 
- variables from `internal_confl` to `ext_conf_minor`: UCDP ACD
- `gtd_`: Global terrorism database
- `ccp_`: Comparative Constitutions Project
- `gmfd_functionallyfree`: media freedom; see SI
- `igo_`: COW IGO membership dataset; see SI
- `NE.TRD.GNFS.ZS`: trade as % of GDP; see SI
- Human rights organization-related (`hro_`); see SI
- Time trends (`year_`); see SI

```{r}
cy <- readRDS("data/cy.rds")
str(cy)
```


## R session info

```{r}
sessionInfo()
```

